---
title: "Quarto Intro"
format: 
  html: 
    execute:
      echo: fenced
editor: visual
---

## Create some data (R):

```{r}
df <- data.frame(temp = rnorm(30, mean = 10, sd = 2),
                pressure = rnorm(30, mean = 6, sd = 1))
```

## Make it available for use in OJS cell:

```{r}
ojs_define(dfjs = df)
```

## Work in JavaScript:

```{ojs}
dfjs_transpose = transpose(dfjs)
```

```{ojs}
dfjs_transpose.filter(d => d.temp > 11)
```

```{ojs}
Plot.plot({
  
  marks: [
    Plot.dot(transpose(dfjs), 
    {x: "temp", y: "pressure", fill: "purple"})
  ]
  
})
```

## Import examples:

The following is imported from the ["Pannable Chart"](https://observablehq.com/@d3/pannable-chart) notebook by Mike Bostock (Copyright 2019 - 2021 Observable, Inc., available by ISC License).

```{ojs}
import {chart as panchart} from "@d3/pannable-chart"
```

```{ojs}
panchart
```


The following is imported from the ["Summary Table"](https://observablehq.com/@observablehq/summary-table) notebook by Mike Freeman (Copyright 2021 Observable, available by ISC License). 

```{ojs}
import {viewof summary_data} from "@observablehq/summary-table"
viewof summary_data
```

## Extras if time:  

-   Visual editor
-   Citations
-   Layouts (e.g. columns, plots in margin, full width)
